A Large-Scale Study of the Use of Eval in R

### 2020-11-26 inst/analysis/environments.Rmd

---
title: "Empirical Evaluation of eval in R"
author: "Pierre Donat-Bouillud"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
---

@@

```{r packages}

```

@@

We distinguish between 4 main categories of `eval` calls with respect to their `envir` argument:

- `envir` is not provided explicitly (and thus is the default argument, which semantically belongs to the absolute category)
- `envir` is a list or a data frame
- `envir` comes from an argument of the caller function
- `envir` is absolutely computed (with `parent.frame()` or equivalent)

@@

@@

@@

```{r envir_list}
eval_calls_env_list <- eval_calls_explicit %>% filter(envir_type == "VECSXP")
```

@@

```{r envir_arg_caller}
eval_calls_arg_caller <- eval_calls_explicit %>% filter(!is.na(envir_from_arg))
```

@@

But all those strange calls are due to Rcpp:

```{r arg_call_rcpp}
eval_calls_arg_caller %>% filter(envir_from_arg > 1, !str_detect(expr_expression, "C\\+\\+Constructor|C\\+\\+Field|C\\+\\+OverloadedMethods")) 
```

@@

```{r envir_absolute}
eval_calls_absolute <- eval_calls_explicit %>% anti_join(eval_calls_env_list) %>% anti_join(eval_calls_arg_caller)
```

@@

>>>>

---
title: "Empirical Evaluation of eval in R"
author: "Pierre Donat-Bouillud"
output:
  html_document:
        code_folding: hide
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
---

@@

```{r packages}
nb_eval_calls <- count(eval_calls, wt = nb_ev_calls)

nb_call_sites <- nb_eval_call_sites(eval_calls)
```

@@

We distinguish between 5 main categories of `eval` calls with respect to their `envir` argument:

- `envir` is not provided explicitly (and thus is the default argument, which semantically belongs to the absolute category)
- `envir` in an eval call generated by Rcpp
- `envir` is a list or a data frame
- `envir` comes from an argument of the caller function
- `envir` is absolutely computed (with `parent.frame()` or equivalent)

@@

nb_default <- count(eval_calls_default, wt = nb_ev_calls)
nb_default_sites <- nb_eval_call_sites(eval_calls_default)

@@

# `envir` with Rcpp

```{r envir_rcpp}
eval_calls_rcpp <- eval_calls_explicit %>% filter(str_detect(expr_expression, "C\\+\\+Constructor|C\\+\\+Field|C\\+\\+OverloadedMethods"))

nb_rcpp <- count(eval_calls_rcpp, wt = nb_ev_calls)
nb_rcpp_sites <- nb_eval_call_sites(eval_calls_rcpp)

eval_calls_explicit <- eval_calls_explicit %>% anti_join(eval_calls_rcpp)
```

@@

```{r envir_list}
eval_calls_env_list <- eval_calls_explicit %>% filter(envir_type == "VECSXP")

nb_env_list <- count(eval_calls_env_list, wt = nb_ev_calls)
nb_env_list_sites <- nb_eval_call_sites(eval_calls_env_list)
```

@@

```{r envir_arg_caller}
eval_calls_arg_caller <- eval_calls_explicit %>% filter(!is.na(envir_from_arg))

nb_arg_caller <- count(eval_calls_arg_caller, wt = nb_ev_calls)
nb_arg_caller_sites <- nb_eval_call_sites(eval_calls_arg_caller)
```

@@

@@

```{r envir_absolute}
eval_calls_absolute <- eval_calls_explicit %>% anti_join(eval_calls_env_list) %>% anti_join(eval_calls_arg_caller)

nb_absolute <- count(eval_calls_absolute, wt = nb_ev_calls)
nb_absolute_sites <- nb_eval_call_sites(eval_calls_absolute)
```

@@

## Summary of the categories

Total eval calls: `r nb_eval_calls`

Total eval call sites: `r nb_call_sites`

- Default: `r nb_default`, call sites: `r nb_default_sites`
- Rcpp: `r nb_rcpp`, call sites: `r nb_rcpp_sites`
- Argument of caller: `r nb_arg_caller`, call sites: `r nb_arg_caller_sites`
- Absolute: `r nb_absolute`, call sites: `r nb_absolute_sites`

### 2020-11-26 inst/paper/main.tex

@@

\title{A Large-Scale Study of the Use of Eval in R}

%\author{Aviral Goel}{Northeastern University, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{goel.aviral@gmail.com}{https://orcid.org/0000-0002-0814-5015}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

%\author{Joan R. Public\footnote{Optional footnote, e.g. to mark corresponding author}}{Department of Informatics, Dummy College, [optional: Address], Country}{joanrpublic@dummycollege.org}{[orcid]}{[funding]}

\authorrunning{J.\,Q. Public and J.\,R. Public} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Aviral Goel, Pierre Donat-Bouillud, Filip Křikava, Christoph Kirsch and Jan Vitek}
% TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

@@

\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords

\category{} %optional, e.g. invited paper

\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversion{A full version of the paper is available at \url{...}.}

\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

\acknowledgements{I want to thank \dots}%optional

%\nolinenumbers %uncomment to disable line numbering

%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

This section presents the results of our empirical study of \eval in R as
answers to four research questions.

@@

@@

\subsection{How Dangerous is eval}

@@

\subsection{Comparison with eval in Javascript}

@@

\subsection{Removing Eval}

>>>>

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{A Large-Scale Study of the Use of Eval in R}
\titlerunning{Eval in R}

\author{Anon}{Under review}{}{}{}
\authorrunning{Anon}
\Copyright{Anon}
\keywords{R, reflection, eval}

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%\
%%%%%%%                                                                         
\EventEditors{Eds.}
\EventNoEds{2}
\EventLongTitle{European Conference on Object Oriented Programming (ECOOP 2021)}
\EventShortTitle{ECOOP 2021}
\EventAcronym{ECOOP}
\EventYear{2021}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

@@

This section presents the results of our empirical study of \eval in R in terms
of four research questions.

@@

\subsection{Necessity of Eval}

@@

\subsection{Power of Eval}

@@

\section{Discussion}

\subsection{Comparison with Javascript}

@@
